The Surprising Runtime Fragility Found when Querying a Single Table

### 2015-04-23 testdata/chunked_column_layouts/draft.tex
!

\begin{table}[!b]
\includegraphics[width=.478\textwidth]{pdf/problem_bests_table.pdf}
\vspace*{-20pt}
\caption{The best layouts and most efficient ways of implementing a given query on a given table and executed on a given machine.}  
\label{fig:problem_bests_table}
%\vspace{-10pt}
\end{table}

@@

@@

\vspace*{-0.2cm}

>>>>

@@

\begin{table}[!b] 
\pivotTable[width=0.478\textwidth, height=0.7478\textwidth, scale=0.666, rows={"Machine", "Table schema", "Query"}, aggregation=Minimum, aggregationattribute=Query time, aggregationBig=Minimum, aggregationattributeBig=Query time (in Sec)]
{SELECT
m.cpuarchitecture AS Machine,
IIF(d.tableschema = '(long a, long b)', 'long', IIF(d.tableschema = '(char a, char b)', 'char', IIF(d.tableschema = '(int a, int b)', 'int', 'n/a')))   AS [Table schema],
IIF(q.querytext = 'SELECT MIN(a+b) FROM t', 'Q1', 'Q2')     AS [Query],
c.compiler      AS Compiler,
c.optlevel      AS [Opt. level],
l.name          AS [Layout name],
CAST(COALESCE(IIF(i.templateparam, 'C', 'R'), 'n/a') AS VARCHAR) AS [Chunk size provided at],
ROUND(v.runtime, 3) 		AS [Query time]
FROM fact_experiment AS v
    JOIN dim_machine m ON m.id = v.machineid
    JOIN dim_dataset d ON d.id = v.datasetid
    JOIN dim_compiler c ON c.id = v.compilerid
    JOIN dim_layout l ON l.id = v.layoutid
    JOIN dim_implementation i ON i.id = v.implementationid
    JOIN dim_query q ON q.id = v.queryid
ORDER BY m.id DESC, d.tableschema, q.querytext,
    c.compiler, c.optlevel, i.templateparam, i.logscaleparam, l.chunksize;}
{SELECT
m.cpu + ' (' +  m.cpuarchitecture + ')' AS Machine,
d.tableschema   AS [Table schema],
q.querytext     AS [Query],
c.compiler      AS Compiler,
c.optlevel      AS [Opt. level],
l.name          AS [Layout name],
CAST(COALESCE(l.chunksize, 'n/a') AS VARCHAR) AS [Chunk size (tuples)],
IIF(i.templateparam, 'Compile time', 'Runtime') AS [Chunk size provided at],
IIF(i.logscaleparam, 'Powers of 2', 'Multiples of 2') AS [Chunk sizes considered],
t.timestamp 	AS [Time of experiment],
ROUND(v.runtime, 3) 		AS [Query time (in Sec)]
FROM fact_experiment AS v
    JOIN dim_machine m ON m.id = v.machineid
    JOIN dim_dataset d ON d.id = v.datasetid
    JOIN dim_compiler c ON c.id = v.compilerid
    JOIN dim_layout l ON l.id = v.layoutid
    JOIN dim_implementation i ON i.id = v.implementationid
    JOIN dim_query q ON q.id = v.queryid
    JOIN dim_time t ON t.id = v.timeid
ORDER BY m.id DESC, d.tableschema, q.querytext,
    c.compiler, c.optlevel, i.templateparam, i.logscaleparam, l.chunksize;}
\vspace*{-5pt}
\caption{The best layouts and most efficient ways of implementing a given query on a given table and executed on a given machine.}  
\label{fig:problem_bests_table}
\vspace{-10pt}
\end{table}

@@

\vspace*{-0.15cm}
